Ecuador plant species GBIF

### 2022-10-31 code/L0/L0_Ecuador_plants_GBIF.Rmd
add summary with summarytools package

```{r}
# using summarytools package
dfSummary(d, 
          plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")
```

>>>>

```{r}
# using summarytools package
dfSummary(d, 
          plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")
d_summary <- dfSummary(d, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(d_summary, method = "render")
view(d_summary, file = file.path(output_path,"Ecuador_GBIF_occurences_summary.html"))
```
